Hunting the Parent of the Orphan Stream: The First High-Resolution Spectroscopic Analysis

### 2013-08-13 2012-oss-hrs/draft-oss.tex
Up to date

\usepackage{verbatim} % for comment blocks
\usepackage{pdflscape} % landscape tables

\shorttitle{First HRS Analysis on the Orphan Stream}
\shortauthors{Casey et al}

@@

\title{The First High-Resolution Spectroscopic Analysis on the Orphan Stream}

\author{Andrew R. Casey\altaffilmark{1,2}, Stefan C. Keller\altaffilmark{1}, Frebel, Anna\altaffilmark{2}, Gary Da Costa\altaffilmark{1}, Elizabeth Maunder\altaffilmark{1}}
\altaffiltext{1}{Research School of Astronomy \& Astrophysics, Australian National University, Mount Stromlo Observatory, via Cotter Rd, Weston, ACT 2611, Australia; \email{arcasey@mso.anu.edu.au}}
\altaffiltext{2}{Massachusetts Institute of Technology, Kavli Institute for Astrophysics and Space Research,
77 Massachusetts Avenue, Cambridge, MA 02139, USA}

\begin{abstract}
test
\end{abstract}

@@

% galactic structure, accretion, build up of galaxies
In the last decade the importance of hierarchical merging for the formation of galaxies has become unambiguously clear. In $\Lambda$CDM cosmology, small clusters conglomerate together to form dwarf galaxies. If these dwarf galaxies become sufficiently close to larger galaxies, they begin infalling and tidal forces cause a stream of stars to be left in their wake. These disrupted stars accrete onto the Milky Way, contributing to a significant fraction of the halo \citet{Bell;et-al_2008}.

% how streams form
% streams agree with lambda cdm
% streams contribute a significant part to the halo

% dominant streams have been identified by their kinematic signatures 
  The Milky Way is the best laboratory to investigate the extent accretion plays in galaxy formation and evolution. Historically, the signatures of accretion events have been identified either through prominent stellar over-densities [citations needed] or by co-moving groups; numerous spatially coincident stars moving with the same velocity [citations needed]. The kinematics of stars in streams allow us to reconstruct the orbital history of the host and place constraints on the Milky Way potential, including the shape and extent of dark matter in the Galaxy [citation needed].

% wealth of data provided by SDSS, allowed orphan stream to be discovered independently
With increasing all-sky survey data being made openly available, searching for stellar over-densities has become extremely efficient [cite koposov]. Using simple color cuts in the SDSS DR5 [citation needed] data set, both \citet{Grillmair_2006} and \citet{Belokurov;et-al_2007} independently discovered the Orphan Stream as a coherent structure spanning over $60^\circ$ in the sky. The Orphan Stream is uniquely distinct from  other stellar streams uncovered in the halo. It has an extremely low surface brightness and is only $\approx2^\circ$ wide \--- which is significantly narrower than other structures found in the Field of Streams \citep{Belokurov;et-al_2006} like Sagittarius ($15^\circ$ wide; [citation needed]). Moreover, the Orphan Stream was aptly named by \citet{Belokurov;et-al_2007} because unlike most other streams, no associated host was found in the SDSS data set, and no existing known system has been reliably associated. The Orphan stream extends well past the celestial equator, outside of the SDSS footprint. Unfortunately the stream has a sufficiently low surface density \citet{Newberg;et-al_2010} found prevents it from being detected within the existing SuperCOSMOS survey \citep{Hambly;et-al_2001}. It is unlikely that this region will be adequately imaged until the SkyMapper telescope commences the Southern Sky Survey \citep{Keller;et-al_2007}. At least until then, it remains a orphaned stream without a parent system.

  % Should I discuss the observational bias, e.g. that we need the smaller ones to really start to pinpoint down the MW potential?

% orphan stream is aptly named and is unique to all other streams. the parent remains lost, although a lot of work has been put in to associating the stream
In the absence of observational data to identify an undiscovered parent host, there has been much effort on associating the Orphan Stream with an existing Milky Way satellite [citations needed]. Given the XX and XX, it is likely the parent host is a dwarf spheroidal galaxy [citations needed], although \citet{Grillmair_2006} predicts the host to be completely disrupted. In the search for an associated system, \citet{Belokurov;et-al_2007} first demonstrated that the Complex A, Ruprecht 106, and Palomar 1 all lie on the same great circle path of the Orphan stream, speculating some association between the four.

% Let's deal with the Complex A controversy first
A detailed analysis on the Orphan Stream orbit is required to examine any potential associations. Kinematics and/or proper motions are required to adequately determine an orbit.
\citet{Belokurov;et-al_2007} listed admittedly two tenuous kinematic observations along the stream, one of which it later appears was erroneous.

% talk about fellhauer

Using these measurements \--- the best, and only at the time \--- and assuming Complex A and the Orphan Stream shared the same orbit, \citet{Jin;Lynden-Bell_2007} found a representative orbit to match observations. Unfortunately their predicted heliocentric velocities that were inconsistent with \citet{Fellhaur;et-al_2007} and later observations by \citet{Newberg;et-al_2010}. Moreover, distances estimated by \citet{Jin;Lynden-Bell_2007} were under-predicted by a factor of three.

In contrast to these simulations, \citet{Sales;et-al_2007} using a X found an orbit which reproduced the velocities, positions and characteristics of the stream, but found no evidence of association with Complex A, or UMaII. 
Their findings indicate that the parent system is likely to be dark matter dominated, and have similar characteristics to some of the Milky Way dwarfs already known (XX, XX and XX). Only self-gravitating systems dominated by dark matter can survive sufficiently long enough to form a stream stretching $\approx55^\circ$ across the sky.

% talk more about Sales

As the SEGUE [acronym needed] data became available, \citet{Newberg;et-al_2010} employed a detailed selection method in order to identify BHB stars in the SDSS data sample.
% blah blah blah

% perhaps mention Sales et al explaining how low surface brightness streams cant be found without spectroscopic surveys

More recently, \citet{Keller;et-al_2012} targeted FGK giants on the Southern end of the SDSS footprint. As the stream crosses the celestial equator it is closest to us and the surface brightness peaks, making it an ideal place to identify stream members. Using inclusive SDSS cuts they targeted hundreds of stars with medium resolution spectroscopy. By identifying likely stream giants based on kinematics and surface gravity estimates, they identified X likely Orphan Stream giants. In this paper we present a detailed chemical analysis on five of those members using high resolution spectroscopic data from the Magellan Clay telescope. Details regarding the observations are outlined in Section \ref{sec:observations}, followed by X.

\section{Observations}
We present high resolution follow-up observations using the Magellan Inamori Kyocera Echelle (MIKE) spectrograph.

% details of the resolution that MIKE provides, etc

\subsection{Target Selection}
% this is double-up
The Orphan Stream has an extremely low surface brightness [citations needed] of XX, and there is a well-described distance gradient along the Orphan stream \citep{Belokurov;et-al_2007,Newberg;et-al_2010}. Therefore the best place to identify stream members within the SDSS sky coverage is near the celestial equator where the stream is closest to us, right at the edge of the SDSS footprint.

\subsection{High Resolution Observations}

\begin{deluxetable*}{lccccccc}
\tablecolumns{2}
\tabletypesize{\scriptsize}
\tablecaption{Observed Targets\label{tab:observed-targets}}
\tablehead{
	\colhead{Star} &
	\colhead{$\alpha$} &
	\colhead{$\delta$} &
	\colhead{Air mass} &
	\colhead{S/N\tablenotemark{a}} &
	\colhead{$V_{\mbox{helio}}$} &
	\colhead{Comment} \\
 & (J2000) & (J2000) & & (px$^{-1}$) & (km s$^{-1}$) &
}
\startdata
HD 136316 & 15 22 17.2 & $-$53 14 13.9 & 1.118 & 335 & $-38.2 \pm 1.1$       & \\
HD 141531 & 15 49 16.9 &\phs09 36 42.5 & 1.309 & 280 & $\phn\phn2.6 \pm 1.0$ & \\
HD 142948 & 16 00 01.6 & $-$53 51 04.1 & 1.107 & 271 & $\phn30.3 \pm 0.9$    & \\
HD 41667  & 06 05 03.7 & $-$32 59 36.8 & 1.005 & 272 & $297.8 \pm 1.7$       & \\
HD 44007  & 06 18 48.6 & $-$14 50 44.2 & 1.033 & 239 & $163.4 \pm 1.3$       & \\
HD 47536  & 06 37 47.7 & $-$32 20 20.1 & 1.002 & 257 & $\phn78.9 \pm 1.2$    & \\
HD 76932  & 08 58 44.2 & $-$16 07 54.2 & 1.158 & 289 & $119.2 \pm 1.2$       & \\
HD 84903  & 09 47 19.3 & $-$41 27 04.9 & 1.260 & 294 & $\phn77.7 \pm 1.4$    & \\
HD 59984  & 07 32 05.7 & $-$08 52 56.1 & 1.111 & 402 & $\phn55.7 \pm 0.5$    & \\
HD 60060  & 07 29 59.6 & $-$52 39 04.3 & 1.127 & 414 & $\phn25.6 \pm 1.1$    & \\
HD 60228  & 07 30 30.8 & $-$54 23 58.6 & 1.139 & 338 & $\phn48.6 \pm 1.7$    & \\
OSS 1     & 10 46 50.6 & $-$00 13 17.9 & 1.363 &  48 & $218.2 \pm 1.7$       & \\
OSS 2     & 10 47 17.8 &\phs00 25 06.9 & 1.995 &  59 & $222.2 \pm 1.3$       & \\
OSS 3     & 10 47 30.3 & $-$00 01 22.6 & 1.156 &  49 & $226.4 \pm 1.3$       & \\
OSS 4     & 10 49 08.3 &\phs00 01 59.3 & 1.881 &  48 & $227.5 \pm 2.1$       & Poor seeing\\
OSS 5     & 10 50 33.7 &\phs00 12 18.3 & 1.295 &  31 & $249.0 \pm 2.6$       & Poor seeing \\
HR 6141   & 16 30 12.3 & $-$25 06 52.0 & 1.003 & 406 & \nodata               & Telluric
\enddata
\tablenotetext{a}{S/N measured at 6000 \AA{} for each target.}
\end{deluxetable*}

% HDs 59984, 76932, 136316, 84903, 44007, 142948
% OS 2,4,5,6,8 (file name convention) here is OS 1,2,3,4,5

\subsection{Data Reduction}

The data were reduced using the latest version of the MIKE pipeline outlined in \citet{Kelson;2003}. For comparison we also reduced our HD 59984 spectra using standard methods in \textsc{IRAF} and found no noteworthy difference between the reduced products. Individual frames for each object were co-added before analysis. We carefully normalised every echelle order using cubic splines. Overlapping normalised orders on each CCD were stitched together, such that a continuous normalised spectra from each CCD results. No telluric corrections were made, as they do not affect the spectral regions we are interested in.

\subsection{Radial Velocities}

We measured radial velocities for every target by cross-correlating each normalised red  spectrum with a synthetic template. Our synthetic template was generated in \textsc{MOOG} using an $\alpha$ element enhanced \citet{Castelli-Kurucz;2004} model atmospheres with $T_{eff} = 4500$ K, $\log{g} = 2.5$, [Fe/H] = -1.5 and no convective overshoot. The line list of \citet{Kirby;et-al_2008} was employed to generate spectra between $845$ nm $< \Lambda < 870$ nm. Both the blue and red normalised frames were shifted to rest before measuring equivalent widths. A number of radial velocity and halo standards were observed during this program, and our heliocentric velocities agree excellently with literature values (Table \ref{tab:observed-targets}).

\subsection{Line List}
\label{sec:line-list}

% table

\subsection{Line Measurements}
An automatic routine has been developed to determine the local continuum and robustly measure the equivalent width of an absorption line. First, we estimate the local continuum surrounding the rest wavelength (Table \ref{tab:line-list}) by iteratively fitting a low order polynomial to $10$ \AA{} either side of the rest wavelength, and clipping only extreme outliers. This process does not determine the final local continuum; all we need is an initial estimate.

Given a rest wavelength and our local continuum estimate, a Gaussian absorption profile is fitted in an iterative process. During this process we have three free parameters: the rest wavelength, the FWHM of the Gaussian profile, and the flux level at the profile trough. The initial value for the minimum flux is taken as the flux level at rest wavelength, and 0.1 \AA{} is used as the initial FWHM for the Gaussian profile. The actual FWHM of our final profile and the subsequent equivalent width measured is largely independent of the initial FWHM provided; only an initial guess is required to decrease computational cost. The difference between our calculated profile and the actual flux is calculated at each iteration, and we use least-squares minimisation to arrive at the best fitting line profile.

Once this process is complete, we use the measured line FWHM in order to decide where the true continuum surrounding the line should start. Again, we iteratively fit a low order polynomial to the surrounding $10$ \AA{} \--- excluding $3\sigma$ of our measured profile\footnote{Recall that FWHM $\approx 2.355\sigma$} \--- but in this step the outlier clipping is more involved: after each iteration we identify flux points as outliers if $>2.5-\sigma$, and we identify sequentially occurring outlier points as probable minima of an absorption line. At each group of outlier points we attempt to fit a Gaussian absorption profile in the same process described above. If a profile is successfully fitted, then we exclude all points within $3-\sigma$ of the detected line from any more continuum determination. In this process, absorption lines are automatically detected and excluded, leaving only the continuum.

When multiple lines are measured from our line list there are stringent quality constraints put in place to eliminate false positive measurements: the final rest wavelength must be within <$10$ \AA{} to the initial guess, the FWHM of each line should be reasonable with respect to all other lines, and the $\chi^2$ difference between the final profile and the spectrum must be reasonable. The $\chi^2$ constraint helps identify measurements where nearby lines are blended.

For spectra which has been perfectly normalised and has high S/N, the method described here will always find the continuum to be unity. For low S/N objects, or where the normalisation is sub-par, our technique robustly determines the true local continuum. We must stress that this process is not 'blind'; the profile and local continuum determination for every measured line has been carefully inspected by the authors. All false positive measurements were discarded during the inspection process, and no lines required manual re-measurement.

%We have verified the accuracy of our automatically determined equivalent widths in two ways:
We have verified the accuracy of our automatically determined equivalent widths both internally and externally. For an internal comparison we have compared careful hand measurements of the equivalent widths against those determined automatically for two stars: the bright metal-rich dwarf HD 59984, and our metal-poor giant target OSS 4. The results of this comparison are shown in Figures \ref{fig:hd59984-ew-comparison} and \ref{fig:oss4-ew-comparison}, and demonstrate our measurement code at varying S/N. HD59984 has a S/N $\approx XX$ px$^{-1}$ at 600 nm, and the difference between equivalent width measurement methods is negligible. Our target star OSS 4 has a much more modest S/N of $\approx50$ px$^{-1}$ at 600 nm, and the two techniques still agree excellently.

These internal comparisons validate the effectiveness of the local continuum fitting within a wide bracket of S/N ratios. To verify our equivalent width accuracy to an external source, we have automatically measured equivalent widths for the metal-poor sub-giant HD140283 and compared our measurements to those of \citet{Norris;et-al_1996}.

The comparison is shown in Figure \ref{fig:norris-ew-comparison}, and the two techniques agree excellently. There is a systematic offset of XX m\AA{} and random scatter of YY m\AA{} between the two techniques. We are confident that our automatic measurement technique can reliably determine equivalent width measurements that are consistent with the literature, over a wide range of evolutionary phases, metallicities and signal quality.

\subsection{Stellar Parameters}

\subsubsection{Effective Temperature}

\subsubsection{Surface Gravity}

\subsection{Uncertainty Analysis}

>>>>

\usepackage{amssymb} % for resolution symbol
\usepackage{verbatim} % for comment blocks
\usepackage{pdflscape} % landscape tables

\shorttitle{The First High-Resolution Spectroscopic Analysis of the Orphan Stream}
\shortauthors{Casey et al}

@@

\title{Hunting the Parent of the Orphan Stream: The First High-Resolution Spectroscopic Analysis}

\author{Andrew R. Casey\altaffilmark{1}, Stefan C. Keller\altaffilmark{1}, Gary Da Costa\altaffilmark{1}, Frebel, Anna\altaffilmark{2}, and Elizabeth Maunder\altaffilmark{1}}
\altaffiltext{1}{Research School of Astronomy \& Astrophysics, Australian National University, Mount Stromlo Observatory, via Cotter Rd, Weston, ACT 2611, Australia; \email{acasey@mso.anu.edu.au}}
\altaffiltext{2}{Massachusetts Institute of Technology, Kavli Institute for Astrophysics and Space Research,
77 Massachusetts Avenue, Cambridge, MA 02139, USA}

\begin{abstract}

%We present the first high-resolution spectroscopic data for five Orphan Stream candidates, observed with the Magellan Inamori Kyocera Echelle (MIKE) spectrograph on the Magellan Clay telescope. 
%The candidates were selected from the low-resolution catalog of \citet{casey;et-al_2013a}: 3 high-probability members, 1 medium- and 1 low-probability stream candidate. Inferred stellar parameters and chemical abundances from our data indicate the low- and medium-probability target are metal-rich field stars. The remaining three high-probability targets are chemically distinct from our standard field stars.

%If the chemistry displayed in these stars is representative of the Orphan Stream and it's unidentified parent host, we have witnessed a unique chemical indicator that can be used to unambiguously trace the Orphan Stream throughout the Milky Way, and a `smoking gun' for the parent of the Orphan Stream.
\end{abstract}

@@

% Galaxy formation in the context of LambdaCDM cosmology
%	-> Bottom-up formation
%	-> Merging
%	-> In situ/Accretion
%	-> Tidal tails

In $\Lambda$CDM cosmology, structure is formed hierarchically in a bottom-up fashion. Small star clusters conglomerate together to form larger systems like the Milky Way. Many stars within our galaxy have formed in-situ \citep{ELS}, but a significant fraction has been built up by the accretion of smaller systems, particularly in the halo \citep{searle;zinn_1978}. As these satellite systems infall towards the Milky Way potential they are disrupted by tidal forces, causing exterior stars to be strewn in forward and trailing directions as tidal tails or `stellar streams'. The evidence for this hierarchical formation and ongoing accretion in the Milky Way has increased significantly over the last decade \citep{ibata;et-al_1994;belokurov;et-al_2006b}.

% Level of accretion in the Milky Way
%	-> Significant fraction of the halo
%	-> With multi-band photometry across the sky the search for these substructures has become more efficient
%	-> Range of masses of infalling progenitors, enabling comparisons to CDM simulations, cosmology

%These discoveries have demonstrated that the Milky Way is the best laboratory to examine accretion in the context of galaxy formation and evolution. From the pencil-beam survey of \citet{starkenburg;et-al_2009}, they find a lower limit of 10\%  substructure for the halo. In contrast, \citet{bell;et-al_2008} suggest that the entire stellar halo has been formed by the accretion of smaller dwarf satellites. A close examination of high-resolution cosmological simulations suggests this number could exceed $>84$\%. More precise observational constraints await the results of large scale spectroscopic surveys. Irrespective of the overall fraction, it is generally accepted that a considerable amount of the halo has been built up by the disruption of smaller systems.

% Deason
% Sharma & Johnson
% Schlaufman

% The Orphan Stream and its properties
%	-> Detected in the SDSS data set
%	-> Extent on sky
%	-> Stream width
%	-> Implications from the stream width and extent: dark matter dominated, old, metal-poor, velocity dispersion, progenitor mass.

Amongst the known substructures in the halo, the Orphan Stream is particularly interesting. \citet{grillmair_2006} and \citet{Belokurov;et-al_2006} independently discovered the stream, spanning over $60^\circ$ in the sky from Ursa Major in the north to near Sextans in the south. The stream has properties that are unique from other halo substructures. It has an extremely low surface brightness ranging from 32-40\,mag arcsec$^{-2}$, and a full width half-mass of $\sim$700\,pc at a distance of $\sim$20\,kpc, which is approximately $\approx2^\circ$ when projected on the sky \citep{belokurov;et-al_2007,grillmair_2006}. The cross-section and luminosity of the stream are directly related to the mass and velocity dispersion of the parent satellite \citep{johnston_1998}. The Orphan Stream width is significantly broader than every known globular cluster tidal tail \citep{odenkirchen;et-al_2003,grillmair_johnson_2006,grillmair_dionatos_2006a,grillmair_dionatos_2006b} and larger than the tidal diameter of all known globular clusters \citep{harris}. As \citet{grillmair_2006} notes, if the cross-section of the stream is circular, then in a simple logarithmic potential with $v_c = 220$\,km s$^{-1}$ -- a reasonable first-order approximation -- the expected random velocities of stars would be required to be $\Delta{E} > 20$\,km s$^{-1}$ in order to produce the stream width. Such a velocity dispersion is significantly larger than the expected random motions of stars that have been weakly stripped from a globular cluster, implying that the Orphan Stream's progenitor mass must be much larger than a classical globular cluster. Photometry indicates the stream is metal-poor, implying that negligible star formation has occurred since infall began several gigayears ago. For a stream of this length to remain structurally coherent over such a long timescale, the progenitor is also likely to be dark-matter dominated. In their discovery papers, \citet{grillmair_2006} and \citet{belokurov;et-al_2007} concluded that the likely parent of the Orphan Stream is a low-luminosity dwarf spheroidal galaxy.

% Observational efforts
%	-> Belokurov 2007
%	-> Newberg's work on BHB stars
%	-> Distances, velocities, strong distance and velocity gradient
%	-> Casey 2013a metallicities, velocities

\citet{newberg;et-al_2010} were able to map the distance and velocity of the stream across the length of the SDSS catalogue using blue horizontal branch (BHB) and F-turnoff stars. They found the stream distance to vary between 19-47\,kpc. This extended further than the 20-32\,kpc measurements made by \citet{belokurov;et-al_2007}. \citet{newberg;et-al_2010} note an increase in the density of the Orphan Stream near the celestial equator $(l, b) = (253\,^\circ, 49\,^\circ)$, proposing the progenitor may be close to this position. The authors attempted to extend their trace of the stream using the southern SuperCOSMOS data set \citep{supercosmos}, but to no avail; the stream's surface brightness is too low. It is still unclear whether the stream extends deep into the southern sky. \citet{newberg;et-al_2010} note an increase in surface brightness near the celestial equator, but given the stream is closest at the equator \citep{belokurov;et-al_2007}, an increase in stream density may be expected given a constant absolute magnitude. Nevertheless, with SDSS photometry and radial velocities from the SEGUE catalog, \citet{newberg;et-al_2010} were able to derive a prograde orbit with an eccentricity, apogalacticon and perigalacticon of $e = 0.7$, 90\,kpc and 16.4\,kpc respectively. If this orbit is accurate, the ability to trace a stellar stream out to 90\,kpc would make a powerful probe for measuring the galactic potential. From their simulations, \citet{newberg;et-al_2010} find a halo and disk mass of $M(R < 60\,{\rm kpc}) = 2.6 \times 10^{11} M_\odot$, $\sim$60\% lower than that found by \citet{xue;et-al_2008} and \citet{koposov;et-al_2008}, and slightly lower than the virial mass of $7 \times 10^{11} M_\odot$ found by \citet{sales;et-al_2008}.

Metallicities derived from SEGUE low-resolution spectra confirm photometric estimates indicating that the stream is metal-poor. A mean metallicity of [Fe/H]$ = -2.1 \pm 0.1$\,dex is found from BHB stars, with a range extending from $-$1.3 to $\sim-$3\,dex \citep{newberg;et-al_2010}. If F-turnoff stars from that sample are included, the metallicity distribution function extends more metal-rich from $\sim-$3 to $-$0.5\,dex. Since BHB stars only form from low metallicity populations, it is not unexpected for BHB stars to be more metal-poor than F-type giants. 
% Sesar work

The situation is further complicated by halo interlopers and small number statistics, so the full shape of the metallicity distribution function (MDF) is unknown. To this end, \citet{casey;et-al_2013a} observed low-resolution spectroscopy for hundreds of stars towards the stream at the celestial equator. The authors targeted the less numerous K-giants \citep[a mere 1.3 red giant branch stars expected per square degree]{sales;et-al_2008,morrison_1993} and found a very weak detection of the stream from kinematics alone. Using wide selections in velocity, distance, proper motions, metallicities, and surface gravity, they identified highly likely Orphan Stream giants. The velocity dispersion of their candidates is within the observational errors, suggesting the stream is kinematically cold along the line-of-sight. Like \citet{newberg;et-al_2010} (and now additionally confirmed by \citet{sesar;et-al_2013}), they also found an extended range in metallicities of their nine most probable candidates: two stars below $\leq-2.70$ and two stars near $-1.17$\,dex all of which are consistent with stream membership. The mean metallicity of their sample was [Fe/H]$ = -1.63 \pm 0.19$\,dex, with a wide dispersion of $\sigma({\rm [Fe/H]}) = 0.56$\,dex. It appears the Orphan Stream may have an extremely wide range in metallicity, consistent with the stochastic chemical enrichment typically observed in dwarf spheroidal (dSph) galaxies \citep{mateo_1998}.

% Possible associations
%	-> There are a number of globular clusters associated along the great circle path.
%	-> Belokurov speculated some association between UM II and Complex A, suggesting the progenitor is a dSph and the clusters have been flung off
%	-> Complex A models by Jin & Lynden-Bell, but they incorrectly predict velocities and under-estimate distances by a factor of three.
%	-> Ursa Major II simulations do not match
%	-> Rule out all known satellites except for Segue 1

As the name suggests, the Orphan Stream's parent satellite has yet to be found. In an effort to identify a progenitor, a number of systems have been identified along the great circle path of the stream as being plausibly associated with the Orphan Stream. These include the linear Complex A H\,\textsc{i} clouds, as well as the globular clusters Palomar 1, Apr 2, Terzan 7 and Ruprecht 106. The low-luminosity dwarf satellites Segue 1 and Ursa Major II also lie along the great circle, although Segue 1 was considered an extended globular cluster until recently \citep{norris;et-al_2010,simon;et-al_2011}. It is worth noting that streams do not often reside along a great circle from the observer's perspective, nor are they expected to do so. \citet{belokurov;et-al_2007} first noted a possible association between the Orphan Stream, Ursa Major II and Complex A. To that end \citet{Jin;Lynden-Bell_2007} and \citet{fellhaur;et-al_2007} explored the possible association between the Orphan Stream with Complex A and Ursa Major II, respectively. In the best-fitting Complex A model, the predicted heliocentric velocities did not match those found by \citet{belokurov;et-al_2007}, or later observations by \citet{newberg;et-al_2010}. The expected distances were also under-estimated by a factor of $\sim{}3$ compared to observations, making the association with Complex A tenuous at best. In the Ursa Major II scenario, the stream's on-sky position was required to exactly overlap with a previous wrap, a somewhat contrived and unlikely scenario. \citet{newberg;et-al_2010} found that the Ursa Major II-Orphan Stream connection was also not compelling as the stream kinematics were not consistent with the Ursa Major II model.

Simulations involving the Complex A and Ursa Major II associations introduced an a priori assumption that the object (e.g. Ursa Major II or Complex A) was related to the Orphan Stream, and consequently found an orbit to match. In contrast, \citet{sales;et-al_2008} approached the problem by fitting an orbit to a single wrap of the data, without assuming a parent satellite a priori. Their $N$-body simulations were inconsistent with either a Complex A or Ursa Major II association with the Orphan Stream. Instead, the authors favour a progenitor with a luminosity $L \sim 2.3 \times 10^4 L_\odot$ or an absolute magnitude $M_r \sim -6.4$, consistent with the observation by \citet{belokurov;et-al_2007} of $M_r \sim -6.7$. Simulations by \citet{sales;et-al_2008} suggest the progenitor may be similar to the present day `classical' Milky Way dwarfs like Carina, Draco, Leo II or Sculptor, but would be very close to fully disrupted over infall, which they suggest has occurred over the last 5.3 Gyr. Time of infall is a critical inference. Longer timescales produce streams that are too wide and diffuse, whereas shorter timescales do not reproduce the $\sim{}$60\,$^\circ$ stream length. The degeneracies between these simulation parameters are important to note, but in any case there are robust conclusions that can be drawn irrespective of the degeneracies. For example, \citet{sales;et-al_2008} note that a globular cluster has a central density too high ($\sim10^{12} M_\odot$\,kpc$^{-3}$) to be fully disrupted along their Orphan Stream orbit within a Hubble time. Given this constraint and the lower limit on luminosity ($L > 2\times10^5 L_\odot$), a globular cluster progenitor seems unlikely from their models.

In addition to the work by \citet{sales;et-al_2008}, $N$-body simulations by \citet{newberg;et-al_2010} exclude all known halo globular clusters as possible progenitors. They conclude with the postulation of two possible scenarios: the progenitor is an undiscovered satellite located between $(l, b) = (250^\circ, 50^\circ)$ and $(270^\circ, 40^\circ)$, or Segue 1 is the parent system.

Segue 1 is an extremely dark-matter dominated system. In fact, kinematics suggest it is so dark-matter dominated that it has become a prime focus for the detection of direct dark-matter annihilation experiments \citep{dm_dominated}.

Segue 1 itself has an extremely wide range in metallicities, varying from [Fe/H] = X to Y dex.

% Segue 1 association?
%	-> Segue 1 is a dark-matter dominated system
%	-> Velocities and positions
%	-> Does it match the expected L, M values from constraints on models
%	-> Extremely wide metallicity range.

% NGC 2419

Given the extended apogalaction of 90\,kpc in the stream orbit found by \citet{newberg;et-al_2010}, \citet{bruns;kroupa_2011} reasoned the stream may be the tidal tail of the massive globular cluster NGC 2419. This system is the most distant (90 kpc) -- yet one of the most massive (R) and luminous ($M$) -- globular clusters known. It is unlike any other globular cluster in the Milky Way. It's shear distance makes spectroscopic observations challenging, but work by \citet{cohen;et-al} have confirmed photometric observations \citet{photometry_for_ngc2419} that the system is metal-poor ([Fe/H] $= -2?$), and identified a remarkable anti-correlation between Mg and K. The level of magnesium depletion ([Mg/Fe] $= -0.40$\,dex??) is not seen anywhere else in the galaxy, neither has the enhanced potassium enrichment ([K/Fe] = $1.5$\,dex??) at the converse end of this peculiar Mg-K anti-correlation. This is also a difficult pattern to explain with from a nucleosynthesis perspective (A. Karakas, in preparation). If NGC 2419 is the parent of the Orphan Stream then this unprecedented chemical signature ought to exist in disrupted stream members as an example of chemical tagging \citep[e.g. see][]{freeman;bland-hawthorn_2002,de_silva;et-al_2007,wylie-de-boer;et-al_2010,majewski;et-al_2012}.

% For nice formatting, the LaTeX table is here:
\begin{deluxetable*}{lccccccccccc}
\tablecolumns{2}
\tabletypesize{\scriptsize}
\tablecaption{Observations\label{tab:observations}}
\tablehead{
	\colhead{Object} &
	\colhead{$\alpha$} &
	\colhead{$\delta$} &
	\colhead{$g$} &
	\colhead{UT Date} &
	\colhead{UT Time} &
	\colhead{Airmass} &
	\colhead{Exp. Time} &
	\colhead{S/N\tablenotemark{a}} &
	\colhead{$V_{\mbox{hel}}$} &
	\colhead{$V_{\mbox{err}}$} \\
 & (J2000) & (J2000) & (mags) & & & (") & (secs) & (px$^{-1}$) & (km s$^{-1}$) & (km s$^{-1}$)
}
\startdata
HD 41667		& 06:05:03.7	& $-$32:59:36.8	& 		& 2011-03-13	& 23:40:52	& 1.005	& 90			& 272	& 297.8 	& 1.7 \\
HD 44007		& 06:18:48.6	& $-$14:50:44.2	& 		& 2011-03-13	& 23:52:18	& 1.033	& 30 			& 239	& 163.4 	& 1.3 \\
HD 76932		& 08:58:44.2	& $-$16:07:54.2	& 		& 2011-03-14	& 00:16:47	& 1.158	& 23 			& 289	& 119.2 	& 1.2 \\
HD 122563		& 14:02:31.8	& $+$09:41:09.9	\\
HD 136316		& 15:22:17.2	& $-$53:14:13.9	& 		& 2011-03-14	& 09:37:26	& 1.118	& 3060 		& 335	& -38.2	& 1.1 \\
HD 141531		& 15:49:16.9	& $+$09:36:42.5	& 		& 2011-03-14	& 09:52:00	& 1.309	& 9180 		& 280	& 2.6 	& 1.0 \\
HD 142948		& 16:00:01.6	& $-$53:51:04.1	& 		& 2011-03-14	& 09:45:12	& 1.107	& 3060 		& 271	& 30.3 	& 0.9 \\
OSS-3 (1)		& 10:46:50.6	& $-$00:13:17.9	& 17.33 	& 2011-03-14	& 01:51:07	& 1.363	&4$\times$2500	& 48	& 217.9	& 0.9 \\ 
OSS-6 (2)		& 10:47:17.8	& $+$00:25:06.9	& 16.09 	& 2011-03-14	& 00:25:37	& 1.995	&3$\times$1600	& 59	& 221.2	& 0.4 \\ 
OSS-8 (3)		& 10:47:30.3	& $-$00:01:22.6	& 17.25	& 2011-03-14	& 04:44:04	& 1.160	&5$\times$1900	& 49	& 225.9	& 0.5 \\ 
OSS-14 (4)		& 10:49:08.3	& $+$00:01:59.3	& 16.27 	& 2011-03-15	& 00:32:17	& 1.881	&4$\times$1400	& 48 	& 225.1	& 0.3 \\ 
OSS-18 (5)		& 10:50:33.7	& $+$00:12:18.3	& 17.82 	& 2011-03-15	& 02:12:46	& 1.295	&4$\times$2100	& 31 	& 247.8	& 0.6
\enddata
\tablenotetext{a}{S/N measured at 600\,nm for each target.}
\end{deluxetable*}

% What we report here.
In this study we present an analysis of high-resolution spectroscopic observations for five Orphan Stream candidates and seven well-studied field stars with similar stellar parameters for comparison. The observations and data reduction are outlined in Section \ref{sec:observations}. In Section \ref{sec:analysis} we describe the details of our curve-of-growth analysis and spectral synthesis approach to infer stellar parameters and chemical abundances. We discuss the results of our analysis in Section \ref{sec:discussion}, including the implications for association between the Orphan Stream and the two currently alleged stream progenitors: Segue 1 and NGC 2419. Finally, we conclude in Section \ref{sec:conclusions} with a summary of our findings.

\section{Observations and Data Reduction}
\label{sec:observations}

%HD 140283	& 15:43:02.3	& $-$10:56:03.0	&		& 2010-08-06	& 23:02:19	& 1.056	& \nodata		& \nodata			& \nodata \\
%l = 250.21, b = 49.46, Vrad = 222.5 +/- 0.9 km/s, Orphan_Lambda = 19.11, Orphan_Beta = -0.48, Vgsr = 83.96 +/- 0.9 km/s
%l = 249.63, b = 49.99, Vrad = 225.7 +/- 0.4 km/s, Orphan_Lambda = 18.54, Orphan_Beta = -0.16, Vgsr = 89.23 +/- 0.4 km/s
%l = 250.17, b = 49.71, Vrad = 230.9 +/- 0.9 km/s, Orphan_Lambda = 18.98, Orphan_Beta = -0.27, Vgsr = 93.15 +/- 0.9 km/s
%l = 250.56, b = 50.04, Vrad = 229.7 +/- 0.3 km/s, Orphan_Lambda = 19.06, Orphan_Beta = +0.14, Vgsr = 92.65 +/- 0.3 km/s
%l = 250.76, b = 50.41, Vrad = 252.6 +/- 0.6 km/s, Orphan_Lambda = 19.02, Orphan_Beta = +0.53
